Shiny App Manuscript Figures: Aquatic Organisms

### 2022-01-08 App_Nonessential/TeamX_Manuscript_Figures/Manuscript_Figures_TeamX.Rmd
changed colors to match

#Transpose data
transposed_size <- as.data.frame(t(as.matrix(CompletenessSummary_size[2:8]))) %>% #1 is category, 2-6 are variables
  arrange('1nm < 100nm')
#Reassign column names
colnames(transposed_size) <- c("1nm < 100nm", "100nm < 1µm", "1µm < 100µm", "100µm < 1mm", "1mm < 5mm")
#Format as matrix
MissingMatrix_size <- data.matrix(transposed_size)
#build heatmap
map <- pheatmap(MissingMatrix_size,
         main = "Particle Characteristics Reported", #title
         fontsize = 12,
         angle_col = 0,
         cluster_rows = FALSE, cluster_cols = FALSE,
         display_numbers = TRUE,
         fontsize_number = 12,
         number_color = "black",
         number_format = "%.0f%%",
         treeheight_row = 0, treeheight_col = 0, 
         color = c("#EEFFFF", "#BAFFFF", "#88E7FF", "#55B4CC", "#3B9AB2", "#228199"))

@@

b <- a %>%
  ggplot(aes(x = year, y = freq, fill = fct_rev(dose_metric))) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  theme_classic()+
  scale_fill_manual(values = c("#3B9AB2", "#EBCC2A", "#F21A00")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,40)) +
  labs(y = "Number of Studies", x = "Year", fill = "Concentration Metric") +
  theme(text = element_text(size = 12), legend.position = "top")

@@

a <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(shape_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  filter(org_f %in% c("Crustacea", "Fish", "Mollusca")) %>%  #Select relevant organism groups
  filter(lvl2_f %in% c("Growth", "Body Condition", "Development", "Mortality", "Reproduction")) %>% 
  ggplot(aes(y = shape_f, x = dose.particles.mL.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  scale_x_log10() +
  labs(y = "Morphology", x = "Particles/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#3B9AB2", "#EBCC2A"))

@@

#Panel A (count)
a <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
  ggplot(aes(y = size_f, x = dose.particles.mL.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  scale_x_log10() +
  labs(y = "Size Category", x = "Particles/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#3B9AB2", "#EBCC2A"))

@@

#Panel B (mass)
b <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
  ggplot(aes(y = size_f, x = dose.mg.L.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  scale_x_log10() +
  labs(y = "Size Category", x = "µg/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#3B9AB2", "#EBCC2A"))

@@

count_plot <- predictions_t1_large %>% 
ggplot(aes(x = est, y = percent/100, color = size)) +
  geom_line(size = 1) +
  geom_xribbon(aes(xmin = lcl, xmax = ucl, y = percent/100, fill = size),color = "black", alpha = 0.15) +
  geom_point(data = points_t1_large,aes(x = Conc, y =frac, color = size)) + 
  # scale_color_tron(name = "Size Bins") +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#F2AD00", "#5BBCD6"),name = "Size Bins") +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#F2AD00", "#5BBCD6"),name = "Size Bins") +
  # scale_fill_tron(name = "Size Bins") +
  guides(fill = FALSE) + # suppress different legend for colors and lines
  coord_trans(x = "log10") +
      scale_x_continuous(limits = c(1e-5, 1e25),
                         breaks = scales::trans_breaks(
                           "log10", function(x) 10^x, n = 10),
                         labels = trans_format(
                           "log10", scales::math_format(10^.x))) +
  scale_y_continuous("Species Affected (%)", 
                     labels = scales::percent, 
                     limits = c(0,1)) +
  labs(x = "Particles/mL") +
  theme_classic()+
  theme(text = element_text(size = 12))

@@

mass_plot <- predictions_t1_large %>% 
ggplot(aes(x = est, y = percent/100, color = size)) +
  geom_line(size = 1) +
  geom_xribbon(aes(xmin = lcl, xmax = ucl, y = percent/100, fill = size),color = "black", alpha = 0.15) +
  geom_point(data = points_t1_large,aes(x = Conc, y =frac, color = size)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#F2AD00", "#5BBCD6"),name = "Size Bins") +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#F2AD00", "#5BBCD6"),name = "Size Bins") +
  guides(fill = FALSE) + # suppress different legend for colors and lines
  coord_trans(x = "log10") +
      scale_x_continuous(limits = c(1e-15, 1e15),
                         breaks = scales::trans_breaks(
                           "log10", function(x) 10^x, n = 10),
                         labels = trans_format(
                           "log10", scales::math_format(10^.x))) +
  scale_y_continuous("Species Affected (%)", 
                     labels = scales::percent, 
                     limits = c(0,1)) +
  labs(x = "µg/mL") +
  theme_classic()+
  theme(text = element_text(size = 12))

>>>>

#Transpose data
transposed_size <- as.data.frame(t(as.matrix(CompletenessSummary_size[2:8]))) %>% #1 is category, 2-6 are variables
  arrange('1nm < 100nm')
#Reassign column names
colnames(transposed_size) <- c("1nm < 100nm", "100nm < 1µm", "1µm < 100µm", "100µm < 1mm", "1mm < 5mm")
#Format as matrix
MissingMatrix_size <- data.matrix(transposed_size)
#build heatmap
map <- pheatmap(MissingMatrix_size,
         main = "Particle Characteristics Reported", #title
         fontsize = 12,
         angle_col = 0,
         cluster_rows = FALSE, cluster_cols = FALSE,
         display_numbers = TRUE,
         fontsize_number = 12,
         number_color = "black",
         number_format = "%.0f%%",
         treeheight_row = 0, treeheight_col = 0, 
         color = c('#d73027','#fc8d59','#fee090','#e0f3f8','#91bfdb','#4575b4'))

@@

b <- a %>%
  ggplot(aes(x = year, y = freq, fill = fct_rev(dose_metric))) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  theme_classic()+
  scale_fill_manual(values = c('#d73027','#fee090','#4575b4')) +
  scale_y_continuous(expand = c(0,0), limits = c(0,40)) +
  labs(y = "Number of Studies", x = "Year", fill = "Concentration Metric") +
  theme(text = element_text(size = 20), legend.position = "top")

@@

a <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(shape_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  filter(org_f %in% c("Crustacea", "Fish", "Mollusca")) %>%  #Select relevant organism groups
  filter(lvl2_f %in% c("Growth", "Body Condition", "Development", "Mortality", "Reproduction")) %>% 
  ggplot(aes(y = shape_f, x = dose.particles.mL.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  scale_x_log10() +
  labs(y = "Morphology", x = "Particles/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#fee090", '#4575b4'))

@@

#Panel A (count)
a <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
  ggplot(aes(y = size_f, x = dose.particles.mL.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  scale_x_log10() +
  labs(y = "Size Category", x = "Particles/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#fee090", '#4575b4'))

@@

#Panel B (mass)
b <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
  ggplot(aes(y = size_f, x = dose.mg.L.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  scale_x_log10() +
  labs(y = "Size Category", x = "µg/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#fee090", '#4575b4'))

@@

count_plot <- predictions_t1_large %>% 
ggplot(aes(x = est, y = percent/100, color = size)) +
  geom_line(size = 1) +
  geom_xribbon(aes(xmin = lcl, xmax = ucl, y = percent/100, fill = size),color = "black", alpha = 0.15) +
  geom_point(data = points_t1_large,aes(x = Conc, y =frac, color = size)) + 
  # scale_color_tron(name = "Size Bins") +
  scale_fill_manual(values = c('#d7191c','#fdae61','#abd9e9','#2c7bb6'),name = "Size Bins") +
  scale_color_manual(values = c('#d7191c','#fdae61','#abd9e9','#2c7bb6'),name = "Size Bins") +
  # scale_fill_tron(name = "Size Bins") +
  guides(fill = FALSE) + # suppress different legend for colors and lines
  coord_trans(x = "log10") +
      scale_x_continuous(limits = c(1e-5, 1e25),
                         breaks = scales::trans_breaks(
                           "log10", function(x) 10^x, n = 10),
                         labels = trans_format(
                           "log10", scales::math_format(10^.x))) +
  scale_y_continuous("Species Affected (%)", 
                     labels = scales::percent, 
                     limits = c(0,1)) +
  labs(x = "Particles/mL") +
  theme_classic()+
  theme(text = element_text(size = 12))

@@

mass_plot <- predictions_t1_large %>% 
ggplot(aes(x = est, y = percent/100, color = size)) +
  geom_line(size = 1) +
  geom_xribbon(aes(xmin = lcl, xmax = ucl, y = percent/100, fill = size),color = "black", alpha = 0.15) +
  geom_point(data = points_t1_large,aes(x = Conc, y =frac, color = size)) +
  scale_fill_manual(values = c('#d7191c','#fdae61','#abd9e9','#2c7bb6'),name = "Size Bins") +
  scale_color_manual(values = c('#d7191c','#fdae61','#abd9e9','#2c7bb6'),name = "Size Bins") +
  guides(fill = FALSE) + # suppress different legend for colors and lines
  coord_trans(x = "log10") +
      scale_x_continuous(limits = c(1e-15, 1e15),
                         breaks = scales::trans_breaks(
                           "log10", function(x) 10^x, n = 10),
                         labels = trans_format(
                           "log10", scales::math_format(10^.x))) +
  scale_y_continuous("Species Affected (%)", 
                     labels = scales::percent, 
                     limits = c(0,1)) +
  labs(x = "µg/mL") +
  theme_classic()+
  theme(text = element_text(size = 12))
